graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-05-01 paper/paper.Rmd
correct figure 2-4 formatting for heatmaps

@@

#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)),
              sub = "(e) Simulated expression data (log scale)", cex.sub = 1.75)
```

>>>>

```{r, include=FALSE, eval=FALSE}
graphics::layout(matrix(c(1:5, 5), nrow = 3, byrow = TRUE))
```

@@

#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)),
sub = "(e) Simulated expression data (log scale)", cex.sub = 1.75,
xlim = c(-0.5, 1.5))
```
